\LARGE \bf A Pipeline for Assembling Collision and Near-Collision Dashcam Footage Datasets

### 2021-03-31 paper.tex
cropped and styled pie charts

\documentclass[letterpaper, 10 pt, conference]{ieeeconf}
\overrideIEEEmargins												% Needed to meet printer requirements.
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{tikz}
\usetikzlibrary{positioning,fit,arrows.meta,backgrounds}
\usepackage{amsmath, amssymb, xcolor, tikz, pgfplots, pgfplotstable}

@@

\begin{figure}[htpb]
	\centering
    \tikzset{
    	node distance = 6m and 0cm,
        module/.style={%
            draw, rounded corners,
            minimum width=#1,
            minimum height=7mm,
            font=\sffamily
            },
        module/.default=1cm,
        >=LaTeX
    }
    \begin{tikzpicture}[
      % This will show the frame around the figure
      show background rectangle]

@@

\begin{figure}[htpb]
		\centering
    \includegraphics[width=3in]{by-collision.png}
		\caption{All videos in database grouped by collision type}
		\label{fig:vids-by-collision}
\end{figure}

\begin{figure}[htpb]
		\centering
    \includegraphics[width=3in]{by-camera.png}
		\caption{All videos in database grouped by camera type}
		\label{fig:vids-by-camera}
\end{figure}

>>>>

\documentclass[letterpaper, 10 pt, conference]{ieeeconf}
\overrideIEEEmargins												% Needed to meet printer requirements.
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{tikz}
\usetikzlibrary{positioning,fit,arrows.meta,backgrounds}
\usepackage{graphicx}
\usepackage{amsmath, amssymb, xcolor, tikz, pgfplots, pgfplotstable}

@@

\begin{figure}[htpb]
	\centering
    \tikzset{
    	node distance = 6mm and 0cm,
        module/.style={%
            draw, rounded corners,
            minimum width=#1,
            minimum height=7mm,
            font=\sffamily
            },
        module/.default=1cm,
        >=LaTeX
    }
    \begin{tikzpicture}[
      % This will show the frame around the figure
      show background rectangle]

@@

\begin{figure}[htpb]
		\centering
    \includegraphics[width=3in,trim={0 1cm 0 1cm},clip]{by-collision.png}
		\caption{All videos in database grouped by collision type}
		\label{fig:vids-by-collision}
\end{figure}

\begin{figure}[htpb]
		\centering
    \includegraphics[width=3in,trim={0 1cm 0 1cm},clip]{by-camera.png}
		\caption{All videos in database grouped by camera type}
		\label{fig:vids-by-camera}
\end{figure}
